### 2020-04-23 ms_8.Rmd
initial

---
title: "ms_8"
author: "Rachel Phan"
date: "4/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(readr)
library(readxl)
library(lubridate)
library(stringr)
library(gganimate)
library(ggplot2)
library(usmap)
library(maps)
library(gganimate)
```

```{r loading data, include=FALSE}

# Obesity data from https://chronicdata.cdc.gov/Nutrition-Physical-Activity-and-Obesity/Nutrition-Physical-Activity-and-Obesity-Behavioral/hn4x-zwk7/data (Center for Disease Control)

obesity_x <- read_csv("Nutrition__Physical_Activity__and_Obesity_-_Behavioral_Risk_Factor_Surveillance_System.csv")

# Food access data from https://www.ers.usda.gov/data-products/food-access-research-atlas/ (United States Department of Agriculture)

food_access <- read_excel("Food Accessibility.xlsx", sheet = 3)

# Rural income data from https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/ (United States Department of Agriculture)

rural_income <- read_csv("Rural Atlas Data/Income.csv")

# Income data for all US Counties from https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/ (US Bureau of Labour Statistics)

income <- read_excel("Unemployment.xls", skip = 4)

# Consumer Price Index ata from https://www.ers.usda.gov/data-products/food-price-outlook/ (United States Department of Agriculture)

cpi <- read_excel("historicalcpi.xlsx", skip = 1)

# What I want to observe here is how different variables affect obesity in the US - income, food accessibility, year, ethnicity, food price, which users can choose from when they pick the graph. Then I want to map out obesity/BMI onto a map of the US. I

# If obesity is affected by food access, then can look deeper into food access. How does ruralness affect food access? How do consumer food price indexes affect food accessibility? How does SNAP policy affect food access (can look at SNAP data from USDA: https://www.ers.usda.gov/data-products/snap-policy-data-sets/).

```

```{r clean obesity data, include=FALSE}

obesity_x <- obesity_x %>% 
    select(YearStart, LocationAbbr, Class, Data_Value, Low_Confidence_Limit, High_Confidence_Limit,
           Sample_Size, "Age(years)", Education, Gender, Income, "Race/Ethnicity")

obesity <- obesity_x %>% 
    rename("state" = LocationAbbr,
           "year" = YearStart,
           "bmi" = Data_Value,
           "conf.low" = Low_Confidence_Limit,
           "conf.high" = High_Confidence_Limit,
           "sample_size" = Sample_Size,
           "age" = "Age(years)",
           "education" = Education,
           "gender" = Gender,
           "class" = Class,
           "race" = "Race/Ethnicity",
           "income" = Income) %>% 
    filter(class == "Obesity / Weight Status",
           !is.na(bmi)) %>% 
    select(-class)

obesity_mean <- obesity %>% 
    group_by(state, year) %>% 
    summarise(mean_bmi = mean(bmi)) %>% 
    filter(state != "US")

plot_usmap(data = obesity_mean, values = "mean_bmi", color = "red", labels = FALSE) + 
    scale_fill_continuous(name = "bmi") + 
    theme(legend.position = "right",
          plot.title = element_text(hjust = 0.5)) + 
    scale_fill_continuous(low = "white", high = "red", name = "BMI") +
    labs(title = "BMI in the US from 2011-2018",
         subtitle = "BMI ",
         caption = "Data from Center for Disease Control") +
    theme_void() +
    transition_time(year)

View(obesity_mean)

```

Shiny App

 fluidPage(

    titlePanel("GOV1005 Final Project"),

    navlistPanel("Header A",
                 tabPanel("Component 1"),
                 "Header B",
                 tabPanel("Component 3"),
                 tabPanel("Component 4")
    ),

    sidebarLayout(position = "right",
        sidebarPanel(img(src = "cartoon.png", height = 140, width = 200)),
        mainPanel(h3("Red Meat Production in the US Over Time"),
                  imageOutput("meat_clean_plot"),
                  br(),
                  br(),
                  br(),
                  br(),
                  br(),
                  br(),
                  actionButton("action", "Click")
    )
)

)

# Define server logic required to draw a histogram
server <- function(input, output) {

    output$meat_clean_plot <- renderImage({
        list(src = "meat_clean_plot.png",
             contentType = 'image/png',
             width = 550,
             height = 500)},
        deleteFile = FALSE
    )  
}

### 2020-04-23 ms_6/app.R

@@ -1,0 +1,51 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+library(shiny)
+library(shinythemes)
+library(tidyverse)
+library(ggplot2)
+
+# ui code
+
+h3("Red Meat Production")
+
+ui <- navbarPage(
+    
+    title = "TITLE",
+    
+    theme = shinytheme("simplex"),
+    
+    tabPanel(
+        title = "About",
+        fluidPage (
+            fluidRow(
+                h1("Welcome!")
+            )
+        )
+    ),
+    
+    tabPanel(
+        title = "Meat",
+        fluidPage(
+            fluidRow(
+                h1("Welcome!")
+            )
+        )
+    )
+)
+    
+# Server code
+
+server <- function(input, output) {
+    
+}
+
+# Run the application 
+shinyApp(ui = ui, server = server)

### 2020-04-24 ms_8.Rmd
created graphs for obesity data, working on food access data

@@
 
-food_access <- read_excel("Food Accessibility.xlsx", sheet = 3)
+food_access_x <- read_excel("Food Accessibility.xlsx", sheet = 3)
 
@@
            "year" = YearStart,
-           "bmi" = Data_Value,
+           "perc_obese" = Data_Value,
            "conf.low" = Low_Confidence_Limit,
@@
     filter(class == "Obesity / Weight Status",
-           !is.na(bmi)) %>% 
+           !is.na(perc_obese)) %>% 
     select(-class)
+
+```
+
+```{r obesity mean plot, include=FALSE}
 
@@
     group_by(state, year) %>% 
-    summarise(mean_bmi = mean(bmi)) %>% 
+    summarise(mean_perc = mean(perc_obese)) %>% 
     filter(state != "US")
 
-plot_usmap(data = obesity_mean, values = "mean_bmi", color = "red", labels = FALSE) + 
-    scale_fill_continuous(name = "bmi") + 
+obesity_mean_plot <- plot_usmap(data = obesity_mean, values = "mean_perc", color = "red", labels = FALSE) +
     theme(legend.position = "right",
           plot.title = element_text(hjust = 0.5)) + 
-    scale_fill_continuous(low = "white", high = "red", name = "BMI") +
-    labs(title = "BMI in the US from 2011-2018",
-         subtitle = "BMI ",
+    scale_fill_continuous(low = "white", high = "red", name = "Percent Obese") +
+    labs(title = "Percent of Population (age 18+) Classified as Obese or Overweight in the US \n Year: {as.integer(frame_time)}",
+         subtitle = "Percent of population tends to increase as time goes on",
          caption = "Data from Center for Disease Control") +
@@
 
-View(obesity_mean)
+animate(obesity_mean_plot)
+
+anim_save("plots/obesity_mean_usmap.gif", plot = last_animation())
+
+```
+
+```{r obesity by region}
+
+obesity_region <- obesity_mean %>% 
+    mutate(region = case_when(
+        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
+        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
+        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
+                     "LA", "OK", "TX") ~ "South",
+        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West")
+    ) %>% 
+    mutate(year = as.numeric(year)) %>% 
+  mutate(mean_perc = round(mean_perc, digits = 0))
+
+obesity_region_plot <- obesity_region %>% 
+    filter(!is.na(region)) %>%
+    ggplot(aes(color = region, x = year, y = mean_perc)) +
+    geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
+    theme_minimal() +
+    labs(title = "Percent of Population Classified as Obese or Overweight \n in US Over Time by Region",
+         caption = "Data from Center for Disease Control",
+         x = "Mean Percent of Population",
+         y = "Year",
+         color = "Region") +
+    geom_smooth(method = "lm", se = FALSE, formula = y ~ x) +
+    facet_wrap(~ region)
+obesity_region_plot
+
+ggsave("plots/obesity_region_plot.png", plot = last_plot())
+
+```
+
+```{r clean food access data, include=FALSE}
+
+food_access_x <- food_access_x %>% 
+    select(State, County, Urban, POP2010, LILATracts_1And10, PovertyRate, MedianFamilyIncome, LA1and10, LAPOP1_10)
+
+food_access <- food_access_x %>% 
+    rename("state" = State,
+           "county" = County,
+           "popul" = POP2010,
+           "urban" = Urban,
+           "lia_1_10" = LILATracts_1And10,
+           "poverty_rate" = PovertyRate,
+           "med_income" = MedianFamilyIncome,
+           "la_1_10" = LA1and10,
+           "la_popul" = LAPOP1_10) %>% 
+    mutate(urban = as.factor(urban),
+           lia_1_10 = as.factor(lia_1_10),
+           la_1_10 = as.factor(la_1_10))
+
+food_access$state = state.abb[match(food_access$state, state.name)]
+
+View(food_access)
 

### 2020-04-24 ms_8.Rmd
finished plotting data for food_access

@@
 library(gganimate)
+library(scales)
 ```
@@
 
-```{r obesity mean plot, include=FALSE}
+```{r obesity mean by year, include=FALSE}
 
@@
     scale_fill_continuous(low = "white", high = "red", name = "Percent Obese") +
-    labs(title = "Percent of Population (age 18+) Classified as Obese or Overweight in the US \n Year: {as.integer(frame_time)}",
+    labs(title = "Percent of Population (age 18+) Classified as Obese or Overweight in the US \n Year:
+         {as.integer(frame_time)}",
          subtitle = "Percent of population tends to increase as time goes on",
@@
 
-```{r obesity by region}
+```{r obesity by region, include=FALSE}
 
@@
     facet_wrap(~ region)
+
 obesity_region_plot
@@
 
-food_access <- food_access_x %>% 
+food_access_y <- food_access_x %>% 
     rename("state" = State,
@@
            "lia_1_10" = LILATracts_1And10,
-           "poverty_rate" = PovertyRate,
+           "poverty" = PovertyRate,
            "med_income" = MedianFamilyIncome,
@@
 
-food_access$state = state.abb[match(food_access$state, state.name)]
+food_access_y$state = state.abb[match(food_access_y$state, state.name)]
 
-View(food_access)
+food_access <- food_access_y %>% 
+    mutate(region = case_when(
+        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
+        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
+        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
+                     "LA", "OK", "TX") ~ "South",
+        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West")
+    ) %>% 
+    select(-county)
+
+```
+
+```{r mean poverty by state, include = FALSE}
+
+food_poverty_mean <- food_access %>%
+    filter(!is.na(region)) %>% 
+    group_by(state) %>% 
+    summarise(mean_poverty = mean(poverty))
+
+food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
+                                     color = "green", labels = FALSE) +
+    theme(legend.position = "right",
+          plot.title = element_text(hjust = 0.5)) + 
+    scale_fill_continuous(low = "white", high = "green", name = "Mean Poverty Rate") +
+    labs(title = "Poverty Rate in the US",
+         caption = "Data from US Department of Agriculture and 2010 Census Bureau") +
+    theme_void()
+food_poverty_mean_plot
+
+ggsave("plots/food_poverty_plot.png", plot = last_plot())
+
+```
+
+```{r food access lia distribution, include=FALSE}
+
+food_lia <- food_access %>%
+    filter(!is.na(region)) %>% 
+    group_by(state, region) %>% 
+    summarise(perc = sum(lia_1_10 == 1)/n()) %>% 
+    mutate(perc = perc*100) %>% 
+    mutate(perc = round(as.numeric(perc), digits = 0)) %>% 
+    arrange(perc)
+
+# food_lia$perc =  paste(round(100*food_lia$perc, digits = 0), "%", sep="")
+
+food_lia_plot <- food_lia %>% 
+    group_by(region) %>% 
+    ggplot(aes(x = reorder(state, perc), y = perc, fill = region)) +
+    geom_col() +
+    theme_minimal() +
+    theme(axis.text.x = element_text(angle = 65, hjust = 0.3, size = 7),
+          panel.grid.major.x = element_line(color = "white"),
+          plot.subtitle = element_text(size = 8)) +
+    labs(title = "Percent of Counties with a Lack of Food Access",
+         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store",
+         caption = "Data from US Department of Agriculture and 2010 Census Bureau",
+         x = "State",
+         y = "Percent of Counties",
+         fill = "Region")
+
+food_lia_plot
+
+ggsave("plots/food_lia_plot.png", plot = last_plot())
 

### 2020-04-24 ms_8.Rmd
added comments
joined data

@@
 
+# Maybe choose a state to look at its obesity rate change over time
+
 obesity_mean <- obesity %>% 
@@
 food_access_x <- food_access_x %>% 
-    select(State, County, Urban, POP2010, LILATracts_1And10, PovertyRate, MedianFamilyIncome, LA1and10, LAPOP1_10)
+    select(State, County, Urban, POP2010, LILATracts_1And10, PovertyRate, MedianFamilyIncome, 
+           LA1and10, LAPOP1_10, LALOWI1_10)
 
@@
            "urban" = Urban,
-           "lia_1_10" = LILATracts_1And10,
            "poverty" = PovertyRate,
            "med_income" = MedianFamilyIncome,
+           "lia_1_10" = LILATracts_1And10,
            "la_1_10" = LA1and10,
-           "la_popul" = LAPOP1_10) %>% 
+           "lia_pop"= LALOWI1_10,
+           "la_pop" = LAPOP1_10) %>% 
     mutate(urban = as.factor(urban),
@@
 
-# food_lia$perc =  paste(round(100*food_lia$perc, digits = 0), "%", sep="")
+# Maybe could input the region in Shiny and people can play around with that?
 
@@
     group_by(region) %>% 
-    ggplot(aes(x = reorder(state, perc), y = perc, fill = region)) +
+    ggplot(aes(y = reorder(state, perc), x = perc, fill = region)) +
     geom_col() +
     theme_minimal() +
-    theme(axis.text.x = element_text(angle = 65, hjust = 0.3, size = 7),
-          panel.grid.major.x = element_line(color = "white"),
+    theme(axis.text.y = element_text(hjust = 1, size = 5.5),
+          panel.grid.major.y = element_line(color = "white"),
+          panel.grid.minor.y = element_line(color = "white"),
           plot.subtitle = element_text(size = 8)) +
-    labs(title = "Percent of Counties with a Lack of Food Access",
-         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store",
+    labs(title = "Percent of Counties with a Lack of Food Access and Low Income Population",
+         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store Who are Low Income",
          caption = "Data from US Department of Agriculture and 2010 Census Bureau",
-         x = "State",
-         y = "Percent of Counties",
-         fill = "Region")
+         x = "Percent of Counties",
+         y = "State",
+         fill = "Region") +
+    geom_text(aes(label = perc), hjust = -0.3, size = 2)
 
@@
 ggsave("plots/food_lia_plot.png", plot = last_plot())
+
+```
+
+```{r join obesity and food access, include=FALSE}
+
+# compare % of people that're obese to % of people that're lia and la
+
+obesity <- obesity %>% 
+     mutate(region = case_when(
+        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
+        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
+        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
+                     "LA", "OK", "TX") ~ "South",
+        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West")
+    ) %>% 
+    mutate(year = as.numeric(year))
+
+obesity_2011 <- obesity %>% 
+    filter(year == 2011) %>%
+    group_by(state, age, gender, income, race) %>% 
+    summarise(mean_perc_obese = round(mean(perc_obese), digits = 0)) %>% 
+    filter(state != "US" & state != "DC")
+
+food_sum <- food_access %>% 
+    group_by(state, urban) %>% 
+    mutate(total_pop = sum(popul),
+           total_lia_pop = sum(lia_pop),
+           total_la_pop = sum(la_pop),
+           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
+           perc_la = round((total_la_pop/total_pop)*100, digits = 0)) %>% 
+    group_by(state, perc_lia, perc_la, urban) %>% 
+    summarise(mean_poverty = round(mean(poverty), digits = 0)) %>% 
+    filter(!is.na(state))
+
+food_sum <- food_access %>% 
+    group_by(state, urban, lia_pop, la_pop, region) %>% 
+    summarise(total_pop = sum(popul),
+           total_lia_pop = sum(lia_pop),
+           total_la_pop = sum(la_pop),
+           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
+           perc_la = round((total_la_pop/total_pop)*100, digits = 0),
+           mean_poverty = round(mean(poverty), digits = 0)) %>% 
+    select(-total_pop, -total_lia_pop, -total_la_pop, -la_pop, -lia_pop)
+
+joined <- left_join(obesity_2011, food_sum, by = "state")
 

### 2020-04-25 ms_8.Rmd
plots

@@
 knitr::opts_chunk$set(echo = TRUE)
-library(tidyverse)
 library(janitor)
@@
 library(scales)
+library(infer)
+library(broom)
+library(tidyverse)
+library(ggcorrplot)
+library(gt)
 ```
@@
 
+saveRDS(obesity_mean, file = "obesity_mean.RDS")
+
 obesity_mean_plot <- plot_usmap(data = obesity_mean, values = "mean_perc", color = "red", labels = FALSE) +
@@
 
+saveRDS(obesity_region, file = "./obesity_shiny/data/obesity_region.RDS")
+
 obesity_region_plot <- obesity_region %>% 
@@
     geom_jitter(aes(alpha = 0.1), show.legend = FALSE) +
+    theme(panel.grid.major.y = element_blank(),
+          panel.grid.minor.x = element_blank()) + 
     theme_minimal() +
@@
          caption = "Data from Center for Disease Control",
-         x = "Mean Percent of Population",
-         y = "Year",
+         y = "Mean Percent of Population",
+         x = "Year",
          color = "Region") +
@@
 
+saveRDS(food_access, file = "./obesity_shiny/data/food_access.RDS")
+
 ```
@@
 
+saveRDS(food_poverty_mean, file = "./obesity_shiny/data/food_poverty_mean.RDS")
+
 food_poverty_mean_plot <- plot_usmap(data = food_poverty_mean, values = "mean_poverty", 
-                                     color = "green", labels = FALSE) +
+                                     color = "white", labels = FALSE) +
     theme(legend.position = "right",
           plot.title = element_text(hjust = 0.5)) + 
-    scale_fill_continuous(low = "white", high = "green", name = "Mean Poverty Rate") +
+    scale_fill_continuous(low = "white", high = "blue", name = "Mean Poverty Rate") +
     labs(title = "Poverty Rate in the US",
@@
     arrange(perc)
+
+saveRDS(food_lia, file = "./obesity_shiny/data/food_lia.RDS")
 
@@
 
-# compare % of people that're obese to % of people that're lia and la
-
 obesity <- obesity %>% 
@@
 
-food_sum <- food_access %>% 
-    group_by(state, urban, lia_pop, la_pop, region) %>% 
-    summarise(total_pop = sum(popul),
-           total_lia_pop = sum(lia_pop),
-           total_la_pop = sum(la_pop),
-           perc_lia = round((total_lia_pop/total_pop)*100, digits = 0),
-           perc_la = round((total_la_pop/total_pop)*100, digits = 0),
-           mean_poverty = round(mean(poverty), digits = 0)) %>% 
-    select(-total_pop, -total_lia_pop, -total_la_pop, -la_pop, -lia_pop)
-
-joined <- left_join(obesity_2011, food_sum, by = "state")
+joined <- left_join(obesity_2011, food_sum, by = "state") %>% 
+    mutate(region = case_when(
+        state %in% c("CT", "MA", "ME", "NH", "RI", "VT", "NJ", "NY", "PA") ~ "Northeast",
+        state %in% c("IL", "IN", "MI", "OH", "WI", "IA", "KS", "MN", "MO", "NE", "ND", "SD") ~ "Midwest",
+        state %in% c("DC", "DE", "FL", "GA", "MD", "NC", "SC", "VA", "WV", "AL", "KY", "MS", "TN", "AR", 
+                     "LA", "OK", "TX") ~ "South",
+        state %in% c("AZ", "CO", "ID", "MT", "NV", "NM", "UT", "WY", "AK", "CA", "HI", "OR", "WA") ~ "West"),
+        urban = case_when(
+            urban == 0 ~ "urban",
+            urban == 1 ~ "rural")
+    )
 
@@
 
-Shiny App
+```{r relationship between obesity and different variables}
 
- fluidPage(
+sapply(joined, class)
 
-    titlePanel("GOV1005 Final Project"),
+joined <- joined %>% 
+    ungroup() %>% 
+    mutate(age = as.factor(age),
+           gender = as.factor(gender),
+           race = as.factor(race),
+           urban = as.factor(urban),
+           region = as.factor(region))
 
-    navlistPanel("Header A",
-                 tabPanel("Component 1"),
-                 "Header B",
-                 tabPanel("Component 3"),
-                 tabPanel("Component 4")
-    ),
+joined_cor <- joined %>% 
+    mutate("Obesity Rate" = mean_perc_obese,
+           "% Low Income and Food Access" = perc_lia,
+           "% Low Food Access" = perc_la,
+           "Poverty Rate" = mean_poverty) %>% 
+    select("Obesity Rate", "% Low Income and Food Access", "% Low Food Access", "Poverty Rate") %>% 
+    cor()
 
-    sidebarLayout(position = "right",
-        sidebarPanel(img(src = "cartoon.png", height = 140, width = 200)),
-        mainPanel(h3("Red Meat Production in the US Over Time"),
-                  imageOutput("meat_clean_plot"),
-                  br(),
-                  br(),
-                  br(),
-                  br(),
-                  br(),
-                  br(),
-                  actionButton("action", "Click")
-    )
-)
+corrplot <- ggcorrplot(joined_cor, 
+             type = "upper", 
+             colors = c("blue", "white", "blue"),
+             lab = TRUE,
+             lab_size = 4,
+             lab_col = "black",
+             ggtheme = theme_void) +
+             labs(title = "Correlations Between Obesity, \n Poverty, and Food Access")  + 
+             theme(plot.title = element_text(hjust = 0.5, size = 15),
+                   legend.position = "none")
 
-)
+ggsave("plots/corr_plot.png", plot = corrplot)
 
-# Define server logic required to draw a histogram
-server <- function(input, output) {
+```
 
-    output$meat_clean_plot <- renderImage({
-        list(src = "meat_clean_plot.png",
-             contentType = 'image/png',
-             width = 550,
-             height = 500)},
-        deleteFile = FALSE
-    )  
-}
+```{r gt}
+
+#yield a graph showing how the mean percentage of obesity is affected by different variables
+
+bootstrap_joined <- joined %>% 
+  rep_sample_n(size = 50, replace = TRUE, reps = 1000) %>% 
+  group_by(replicate)
+
+saveRDS(bootstrap_joined, file = "./obesity_shiny/data/bootstrap_joined.RDS")
+
+joined_lm_lia <- lm(mean_perc_obese ~ perc_lia, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_lia_gt <- joined_lm_lia %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Low Food Access and Low Income on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+gtsave(joined_lm_lia_gt, "lia_gt.html")
+
+joined_lm_gender <- lm(mean_perc_obese ~ gender, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_gender_gt <- joined_lm_gender %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Gender on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+gtsave(joined_lm_gender_gt, "gender_gt.html")
+
+joined_lm_age <- lm(mean_perc_obese ~ age, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+    select(term, estimate, conf.low, conf.high) %>% 
+    mutate(
+      estimate = round(estimate, digits = 3),
+      conf.low = round(conf.low, digits = 3),
+      conf.high = round(conf.high, digits = 4))
+
+joined_lm_age_gt <- joined_lm_age %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Age on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_lm_race <- lm(mean_perc_obese ~ race, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_race_gt <- joined_lm_race %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Race on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_lm_la <- lm(mean_perc_obese ~ perc_la, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_la_gt <- joined_lm_la %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Low Food Access on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_lm_urban <- lm(mean_perc_obese ~ urban, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_urban_gt <- joined_lm_urban %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Ruralness on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_lm_mean_poverty <- lm(mean_perc_obese ~ mean_poverty, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_poverty_gt <- joined_lm_mean_poverty %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Poverty on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_lm_region <- lm(mean_perc_obese ~ region, data = bootstrap_joined) %>% 
+  tidy(conf.int = TRUE) %>%
+  select(term, estimate, conf.low, conf.high) %>% 
+  mutate(
+    estimate = round(estimate, digits = 3),
+    conf.low = round(conf.low, digits = 3),
+    conf.high = round(conf.high, digits = 4))
+
+joined_lm_region_gt <- joined_lm_region %>% 
+  gt() %>% 
+  tab_header(
+    title = "Effect of Region in the US on Average Percentage of Obesity in a Population") %>%
+  cols_label(
+    term = "Variable", 
+    estimate = "Estimate",
+    conf.low = "Lower Bound",
+    conf.high = "Higher Bound") %>% 
+   tab_spanner(
+    label = "Data from 2010 Census Bureau, USDA, and CDC",
+    columns = vars(term, estimate, conf.low, conf.high))
+
+joined_poverty_obesity <- bootstrap_joined %>% 
+  ggplot(aes(x = mean_poverty, y = mean_perc_obese)) +
+  geom_jitter(aes(color = urban)) +
+  scale_color_manual(values = c("purple", "dark red")) +
+  theme_minimal() +
+  theme(panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank()) +
+  labs(title = "Poverty Rate on Obesity Rate",
+       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
+       color = "Ruralness",
+       x = "Mean Poverty Rate",
+       y = "Mean Obesity Rate") +
+  geom_smooth(method = "lm", color = "black")
+joined_poverty_obesity
+
+```
+
+An Introduction
+
+- Introduce the issue
+- Describe what obesity is 
+- Describe what food insecurity is
+
+Variables in question
+
+Obesity
+Obesity over time map
+Choose region to look at map
+The poverty map
+Should make a graph showing how poverty relates to obesity
+
+Food lia
+Could allow people to choose between which regions they want to compare
+
+Findings
+Correlation plot
+Make best fit line graphs for each variable that affects obesity and allow people to choose which one they want to look at
+Make a regression plot
+  Otherwise, gt tables?
+
+Data
+Give process of creation of the data 
+Give sources
+
+Me
+Self introdcution
+Provide links to github and linkedin

### 2020-04-25 obesity_shiny/app.R

@@ -1,0 +1,272 @@
+#
+# This is a Shiny web application. You can run the application by clicking
+# the 'Run App' button above.
+#
+# Find out more about building applications with Shiny here:
+#
+#    http://shiny.rstudio.com/
+#
+
+
+library(shiny)
+library(shinythemes)
+library(tidyverse)
+library(ggplot2)
+library(usmap)
+library(shinyWidgets)
+
+# read in data from RDS
+
+obesity_region <- readRDS("data/obesity_region.RDS")
+
+
+# ui code
+
+ui <- navbarPage(
+    
+    title = "Obesity and Food Access in the US",
+    
+    theme = shinytheme("cosmo"),
+    
+    tabPanel("An Introduction",
+        fluidPage(
+            
+            br(),
+            br(),
+            
+            imageOutput("obesity_image", width = "100%", height = "100%"),
+            
+            br(),
+            
+            fluidRow(column(2), column(8,
+                     h1(tags$b("Obesity and Food Insecurity in the United States"), align = "center", style = "color: darkred"),
+                     p(tags$b("Insights on America's Alarming Obesity Rates and an Analysis on Food Insecurity"), align = "center"),
+                     
+                     br(),
+                     
+                     p("Although one of the wealthiest countries in the world, The United States has one of the highest obesity rates
+                  of any developed country. In 2016, according to the Central Intelligence Agency, the US saw 36.20% of its 
+                  adult population classified as obese. Granted, the US is an incredibly large and diverse country. People's diets and
+                  amount of physical movement vary region to region, state to state. Thus, It is important to look at the
+                  variation in the percentage of population that is obese across different state."),
+                     
+                     br(),
+                     
+                     h3("Obesity", style = "color: darkred"),
+                     
+                     p("Obesity is defined as excessive or abnormal fat accumulation that may impair health, according to the World
+                  Health Organization. Body Mass Index is one way to determine obesity status; it is calculated by dividng a person's 
+                  weight in kilograms by the square of their height in meters. A BMI equal to or greater than 30 is classified as obese."),
+                     
+                     br(),
+                     
+                     p("Because obesity can make its population more susceptible to severe illnesses, I wanted to explore different 
+                       factors that could affect the percentage of obesity in a population. Some of these variables include, of
+                       course, age, gender, and the region in which you live. However, I was also inspired by the unfortunate situation
+                       that COVID19 has presented us with: food shortages. I wondered if having easy way access to healthy and reliable
[…]

### 2020-04-26 ms_8.Rmd
almost finished. Need to add food access and fix model

@@
 library(gt)
+library(webshot)
 ```
@@
     theme_void()
-food_poverty_mean_plot
 
@@
            region = as.factor(region))
+saveRDS(joined, file = "./obesity_shiny/data/joined.RDS")
 
@@
     cor()
+
+saveRDS(joined_cor, file = "./obesity_shiny/data/joined_cor.RDS")
 
@@
 
-gtsave(joined_lm_lia_gt, "lia_gt.html")
+gtsave(joined_lm_lia_gt, "lia_gt.png")
 
@@
   geom_smooth(method = "lm", color = "black")
-joined_poverty_obesity
+
+joined_demo <- bootstrap_joined %>% 
+  ggplot(aes(x = age, y = mean_perc_obese, color = age)) +
+  geom_jitter() +
+  theme_minimal() +
+  theme(panel.grid.minor.y = element_blank(),
+        panel.grid.minor.x = element_blank(),
+        axis.text.x = element_text(angle = 35, hjust = 1)) +
+  labs(title = "Poverty Rate on Obesity Rate",
+       caption = "Data from US Department of Agriculture and 2010 Census Bureau",
+       color = "Ruralness",
+       x = "Mean Poverty Rate",
+       y = "Mean Obesity Rate")
+joined_demo
 
@@
 
+Food Access
 Food lia
 Could allow people to choose between which regions they want to compare
+Food lia us map
+Allow people to choose between lia and la
 

### 2020-04-26 obesity_shiny/app.R

@@ -18,7 +18,9 @@ library(shinyWidgets)
 # read in data from RDS
 
 obesity_region <- readRDS("data/obesity_region.RDS")
-
+joined_cor <- readRDS("data/joined_cor.RDS")
+bootstrap_joined <- readRDS("data/bootstrap_joined.RDS")
+joined <- readRDS("data/joined.RDS")
 
 # ui code
 
@@ -101,12 +103,19 @@ ui <- navbarPage(
                         tabPanel("The United States",
                             
                         fluidRow(
+                            column(3),
                             
-                                h3("Obesity Across the United States Over Time", style = "color: darkred; text-align: center"),
+                            column(6,
+                                   
+                                br(),
+                                
+                                h2("Obesity Across the United States Over Time", style = "color: darkred; text-align: center"),
+                                
+                                br(),
                                 
                                  p("How does the percentage of the population classified as obese or overweight change over time?
                                     The graphic to the right suggests that the percentage increases over time, looking at years from
-                                    2011-2018. Where does most of the change occur?"),
+                                    2011-2018. Where does most of the change occur?", style = "text-align: center")),
 
                                 ),
                         
@@ -132,7 +141,7 @@ ui <- navbarPage(
                                 br(),
                                 br(),
                                 
-                                pickerInput("region", tags$b("Choose a region:"),
+                                selectInput("region", tags$b("Choose a region:"),
                                             choices = c("West", "South", "Northeast", "Midwest"),
                                             multiple = FALSE)
                                
@@ -145,13 +154,19 @@ ui <- navbarPage(
                
                         br(),
                         br(),
+                        br(),
                         
                         sidebarLayout(
                           sidebarPanel(column(4),
                                        
                                 h3("Obesity Across Regions Comparatively", style = "color: darkred"),          
                                        
-                                p("TEXT HERE")),
+                                br(),
+                                
+                                p("It may be helpful to see how the change in the mean percentage of the population 
+                                  classified as obese or overweight overtime differs region to region. This is easier
+                                  to compare when the graphs are shown side-by-side. It appears the South and the Midwest
+                                  are increasing the fastest, and have also started off the highest as well.")),
                           
                           mainPanel(
                               imageOutput("obesity_region_facet")
@@ -165,9 +180,24 @@ ui <- navbarPage(
                 br(),
                 
                 sidebarLayout(
-                    sidebarPanel(
+                    sidebarPanel(column(3),
                         
[…]

### 2020-04-27 ms_8.Rmd
added in gt tables

@@
 
-# Obesity data from https://chronicdata.cdc.gov/Nutrition-Physical-Activity-and-Obesity/Nutrition-Physical-Activity-and-Obesity-Behavioral/hn4x-zwk7/data (Center for Disease Control)
+# Read in obesity data from
+# https://chronicdata.cdc.gov/Nutrition-Physical-Activity-and-Obesity/Nutrition-Physical-Activity-and-Obesity-Behavioral/hn4x-zwk7/data
+# (Center for Disease Control)
 
@@
 
-# Food access data from https://www.ers.usda.gov/data-products/food-access-research-atlas/ (United States Department of Agriculture)
+# Read in food access data from
+# https://www.ers.usda.gov/data-products/food-access-research-atlas/ (United
+# States Department of Agriculture)
 
@@
 
-# Rural income data from https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/ (United States Department of Agriculture)
+# Read in rural income data from
+# https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/
+# (United States Department of Agriculture)
 
@@
 
-# Income data for all US Counties from https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/ (US Bureau of Labour Statistics)
+# Read in income data for all US Counties from
+# https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/
+# (US Bureau of Labour Statistics)
 
@@
 
-# Consumer Price Index ata from https://www.ers.usda.gov/data-products/food-price-outlook/ (United States Department of Agriculture)
+# REad in consumer Price Index ata from
+# https://www.ers.usda.gov/data-products/food-price-outlook/ (United States
+# Department of Agriculture)
 
@@
 
-# What I want to observe here is how different variables affect obesity in the US - income, food accessibility, year, ethnicity, food price, which users can choose from when they pick the graph.
-Then I want to map out obesity/BMI onto a map of the US.
-I
-
-# If obesity is affected by food access, then can look deeper into food access.
-How does ruralness affect food access?
-How do consumer food price indexes affect food accessibility?
-How does SNAP policy affect food access (can look at SNAP data from USDA: https://www.ers.usda.gov/data-products/snap-policy-data-sets/).
+# Notes for myself: If obesity is affected by food access, then can look deeper
+# into food access. How does ruralness affect food access? How do consumer food
+# price indexes affect food accessibility? How does SNAP policy affect food
+# access (can look at SNAP data from USDA:
+# https://www.ers.usda.gov/data-products/snap-policy-data-sets/).
 
@@
 ```{r clean obesity data, include=FALSE}
+
+# There are a lot of variables that I don't want, so I selected for the ones I
+# do. Then I renamed the variables so they made sense to me. I only want data
+# pertaining to obesity, so I filtered for that and took out the NAs.
 
@@
 
-# Maybe choose a state to look at its obesity rate change over time
+# There are a lot of observations for each state in my data, but I only want the
+# mean percent obesity for each state, so that means one observation for each
+# state. I can do so by summarising my data into a mean percentage of obesity
+# for each state. I only want the states, so I filtered out the US observation.
+# I then saved it to an RDS file to load in Shiny later. Now I want to make a
+# plot that shows the mean percentage of obesity over time on the US map, so I
+# used plot_usmap and then gganimate. scale_fill_continuous lets me choose the
+# legend colours I want. Then I saved it as a file using anim_save.
 
@@
 ```{r obesity by region, include=FALSE}
+
+# I want to group the states by the region of the US they're in, so I used as
+# when. I noticed that year wasn't a numeric variable, so I made it one. Then I
+# rounded the mean percentages of obesity. I wanted to plot the obesity rate by
+# region next. I used geom_jitter because of lot of plot points overlapped. I
+# put in a line of best fit using geom_smooth. I then used ggsave to save my
+# plot as a file.
 
@@
 
-obesity_region_plot
-
 ggsave("plots/obesity_region_plot.png", plot = last_plot())
@@
 ```{r clean food access data, include=FALSE}
+
+# There are a lot of variables that I don't want, so I selected for the ones I
+# do. Then I renamed the variables so they made sense to me. Then I made sure
+# that the variables I want to be factors are factors using mutate. In order to
+# join the data together late by state, I made sure that the states are
+# abbreviated like in the obesity data. I did this using state.abb, which
+# matched the full state names in my dataset to state.names in the base R (I
+# think it's base R). Then I used case_when to group the states into regions. I
+# then saved my data as an RDS file to load into Shiny later.
 
@@
 
+# I want to make a graph based on the mean poverty of each states. I filtered
+# for regions that were not a state and thus yielded NA for region (meaning
+# places like Puerto Rico, Guam, the Virgin Islands, DC, and the US as a whole).
+# I then plotted that data using plot_usmap onto a US map based on state. I then
+# saved that plot using ggsave.
+
 food_poverty_mean <- food_access %>%
@@
 
+# Now I wanted to make a graph based on food access (low income and low food
+# acess). Again, I had a lot of observations per state. I decided to find the
+# percentage of counties in the state that were considered low income and low
+# food access (denoted as a 1 for lia_1_10), so I summed up the total and
+# divided by the number of counties in the state, yielding the percentage of
+# counties in the state that were classified as having 33% or more of its
+# population with low income and low access to food. I changed that to a numeric
+# variable and rounded, arranging from the lowest percentage to the highest. I
+# saved that data into an RDS file. Then I plotted it using geom_col. To reorder
+# the columns from highest to lowest, I used the reorder function. I had the
+# percentage as the x variable rather than the y, even though it is the
+# dependent variable, because I wanted the graph to be flipped since it looked
+# nicer that way. Then I colored the bars by the region. I then saved the graph.
+
 food_lia <- food_access %>%
@@
 saveRDS(food_lia, file = "./obesity_shiny/data/food_lia.RDS")
-
-# Maybe could input the region in Shiny and people can play around with that?
 
@@
     labs(title = "Percent of Counties with a Lack of Food Access and Low Income Population",
-         subtitle = "Lack of Food Access Defined by 33% of the Population Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, Supercenter, or Grocery Store Who are Low Income",
+         subtitle = "Lack of Food Access Defined by 33% of the Population 
+                     Living More Than \n 1 Mile (Urban) Or 10 Miles (Rural) Away from Supermarket, 
+                     Supercenter, or Grocery Store Who are Low Income",
          caption = "Data from US Department of Agriculture and 2010 Census Bureau",
@@
 
-food_lia_plot
-
 ggsave("plots/food_lia_plot.png", plot = last_plot())
@@
 ```{r join obesity and food access, include=FALSE}
+
+# Although I had used case_when to group the states into regions, I had saved
+# that into a different object, so I just did it again t save into the overall
+# obesity dataset. I wanted to join the datasets next. However, obesity
+# originally had a lot of observations based on one state instead of just one
+# observation based on one state each time, so I used summarise to take the mean
+# observations of obesity rates for each state to get it down to just one
+# observation per state. I tried using mutate,  but that kept all the
+# observations intact and just created a new column. Using summarise allowed me
+# to get rid of all the observations I didn't want and just return the mean
+# observation. By grouping by state, age, gender, income, and race, I was able
+# to keep those variables after the summarise. I then filtered for what I didn't
+# want. I then wanted to clean the food_access data before joining. I wanted the
+# percentage of the population in each state (out of the sample size) that was
+# either low income and low food access or just low food access overall, so I
+# summed up the total populations and then use that to divide the sum of the low
+# income and low food access population and the low food access population by. I
+# then used a left join to join the data together (didn't matter which join I
+# used since all the observations matched anyway) and used case_when for region
+# again since I had forgotten to include that before. Then I changed the urban
+# values into values I understood using case_when.
 
@@
 
+# I used sapply to look at the class of each variable of joined, and changed the
+# variables to the class I wanted. I saved that data into an RDS file. Now I
+# want a graph that shows the correlation between multiple variables, so I
+# mutated the names to make sense when they showed up on the graph. I selected
+# for the variables to pipe into cor(). Then I saved that data into an RDS file.
+# I made a correlation plot using the correlation matrix and saved that using
+# ggsave.
+
 sapply(joined, class)
@@
            region = as.factor(region))
+
 saveRDS(joined, file = "./obesity_shiny/data/joined.RDS")
@@
 
-#yield a graph showing how the mean percentage of obesity is affected by different variables
+# Because my data only had 10,000 observations, I wanted to sample my data
+# multiple times again, so I used a bootstrap sampling to get 50,000
+# observations. I saved that data into an RDS file. Since it turns out that
+# there isn't much correlation between food access and obesity, I wanted to find
+# linear regression models for each of my variables and see how how they relate
+# to obesity and they might predict obesity. I did that for low income and low
+# food access, low food access, gender, age, race, poverty, region, and
+# ruralness. Unfortunately, I was unable to map the linear models onto all of my
+# data (there was an error that my object was a double instead of 1, which my
+# CAs also seemed unable to fix during study halls) so I decided to just keep
+# the regression just to my boostrapped data. Then I put the values into gt
+# tables, and will explain what they mean on the Shiny app. In the future, I may
+# also do a regression for all the variables at once after looking at the
+# relationship to obesity. I saved each of the gt tables into an html file.
 
@@
     columns = vars(term, estimate, conf.low, conf.high))
+```
+
+```{r poverty and obesity relationship graph}
 
@@
        y = "Mean Obesity Rate")
-joined_demo
 

### 2020-04-27 ms_6/app.R

@@ -11,6 +11,7 @@ library(shiny)
 library(shinythemes)
 library(tidyverse)
 library(ggplot2)
+library(usmap)
 
 # ui code
 
@@ -18,15 +19,32 @@ h3("Red Meat Production")
 
 ui <- navbarPage(
     
-    title = "TITLE",
+    title = "Obesity and Food Access in the US",
     
     theme = shinytheme("simplex"),
     
     tabPanel(
-        title = "About",
+        title = "Findings",
         fluidPage (
-            fluidRow(
-                h1("Welcome!")
+            
+            imageOutput("obesity_image", width = "100%", height = "100%"),
+            
+            fluidRow(column(2)
+                h1(tags$b("Obesity and Food Access in The United States"), align = "center"),
+                p(tags$em("Insights on America's Alarming Obesity Rates \n and Analysis on Food Access"), align = "center"),
+                
+                br(),
+                br(),
+                
+                p("Although one of the wealthiest countries in the world, The United States has one of the highest obesity rates
+                  of any developed country. In 2016, according to the Central Intelligence Agency, the US saw 36.20% of its 
+                  adult population as obese. Granted, the US is an incredibly large and diverse country. People's diets and
+                  amount of physical movement vary region to region, state to state. It is important to look at the
+                  variation in the percentage of population that is obese by state."),
+                p("Obesity is defined as excessive or abnormal fat accumulation that may impair health, according to the World
+                  Health Organization. Body Mass Index is one way to determine obesity status, and a BMI of equal to or 
+                  greater than 30 is classified as obese. BMI is calculated by a person's weight in kilograms divided by the 
+                  square of the heigh in meters.")
             )
         )
     ),
@@ -44,6 +62,16 @@ ui <- navbarPage(
 # Server code
 
 server <- function(input, output) {
+    
+    # Load in image for top of app for Findings page
+        
+    output$obesity_image <- renderImage({
+        
+        list(src = 'images/obesity.image.jpg', 
+             height = 444,
+             width = 800, style="display: block; margin-left: auto; margin-right: auto;")
+    }, deleteFile = FALSE
+    )
     
 }
 

### 2020-04-27 obesity_shiny/app.R

@@ -14,6 +14,7 @@ library(tidyverse)
 library(ggplot2)
 library(usmap)
 library(shinyWidgets)
+library(ggcorrplot)
 
 # read in data from RDS
 
@@ -21,6 +22,14 @@ obesity_region <- readRDS("data/obesity_region.RDS")
 joined_cor <- readRDS("data/joined_cor.RDS")
 bootstrap_joined <- readRDS("data/bootstrap_joined.RDS")
 joined <- readRDS("data/joined.RDS")
+food_poverty_mean <- readRDS("data/food_poverty_mean.RDS")
+
+bootstrap_joined <- bootstrap_joined %>%
+    mutate(age = as.factor(age),
+           gender = as.factor(gender),
+           race = as.factor(race),
+           urban = as.factor(urban))
+# filter(!is.na(input$demographic))
 
 # ui code
 
@@ -281,10 +290,15 @@ ui <- navbarPage(
                                 br(),
                                 
                                 selectInput("yvariable", tags$b("Outcome Variable:"),
-                                            choices = c("Obesity Rate", "Low Income and Low Food Access", "Low Food Access")),
-                                
+                                            choices = c("Mean Percent Obese" = "mean_perc_obese", 
+                                                        "Mean Percent Low Income and Low Food Access" = "perc_lia", 
+                                                        "Mean Percent Low Food Access" = "perc_la")),
+
                                 selectInput("demographic", tags$b("Demographic Variable:"),
-                                            choices = c("Gender", "Age", "Race", "Ruralness"),
+                                            choices = c("Gender" = "gender", 
+                                                        "Age" = "age", 
+                                                        "Race" = "race", 
+                                                        "Ruralness" = "urban"),
                                             multiple = FALSE),
                             ),
                             
@@ -364,7 +378,7 @@ ui <- navbarPage(
                         
                         column(10,
                         
-                        h2("About me", style = "color: darkred"),
+                        h2("Contact", style = "color: darkred"),
                         
                         br(),
                         
@@ -476,52 +490,54 @@ server <- function(input, output) {
     
     output$demographic <- renderPlot({
         bootstrap_joined <- bootstrap_joined %>%
-            mutate(age = as.factor(age),
-                   gender = as.factor(gender),
-                   race = as.factor(race),
-                   urban = as.factor(urban)) %>%
[…]

### 2020-04-27 ms_8.Rmd
almost finished food access tab

@@
 # https://www.ers.usda.gov/data-products/atlas-of-rural-and-small-town-america/
-# (United States Department of Agriculture)
+# (United States Department of Agriculture). Might not use it.
 
@@
 # https://www.ers.usda.gov/data-products/county-level-data-sets/download-data/
-# (US Bureau of Labour Statistics)
+# (US Bureau of Labour Statistics). Might not use it.
 
@@
 
-# REad in consumer Price Index ata from
+# Read in consumer Price Index ata from
 # https://www.ers.usda.gov/data-products/food-price-outlook/ (United States
-# Department of Agriculture)
+# Department of Agriculture). Might not use it.
 
@@
 
-anim_save("plots/obesity_mean_usmap.gif", plot = last_animation())
+anim_save("obesity_shiny/plots/obesity_mean_usmap.gif", plot = last_animation())
 
@@
 
-ggsave("plots/obesity_region_plot.png", plot = last_plot())
+ggsave("obesity_shiny/plots/obesity_region_plot.png", plot = last_plot())
 
@@
 
-ggsave("plots/food_poverty_plot.png", plot = last_plot())
+ggsave("obesity_shiny/plots/food_poverty_plot.png", plot = last_plot())
 
@@
 
-ggsave("plots/food_lia_plot.png", plot = last_plot())
+ggsave("obesity_shiny/plots/food_lia_plot.png", plot = last_plot())
 
@@
     filter(!is.na(state))
+
+saveRDS(food_sum, file = "./obesity_shiny/data/food_sum.RDS")
 
@@
 
-ggsave("plots/corr_plot.png", plot = corrplot)
+ggsave("obesity_shiny/plots/corr_plot.png", plot = corrplot)
 
@@
 
+gtsave(joined_lm_age_gt, "age_gt.html")
+
 joined_lm_race <- lm(mean_perc_obese ~ race, data = bootstrap_joined) %>% 
@@
     columns = vars(term, estimate, conf.low, conf.high))
+
+gtsave(joined_lm_race_gt, "gender_race.html")
 
@@
 
+gtsave(joined_lm_la_gt, "la_gt.html")
+
 joined_lm_urban <- lm(mean_perc_obese ~ urban, data = bootstrap_joined) %>% 
@@
     columns = vars(term, estimate, conf.low, conf.high))
+
+gtsave(joined_lm_urban_gt, "urban_gt.html")
 
@@
 
+gtsave(joined_lm_poverty_gt, "poverty_gt.html")
+
 joined_lm_region <- lm(mean_perc_obese ~ region, data = bootstrap_joined) %>% 
@@
     columns = vars(term, estimate, conf.low, conf.high))
+
+gtsave(joined_lm_region_gt, "region_gt.html")
+
 ```
@@
 ```{r poverty and obesity relationship graph}
+
+# Because there wasn't really any correlation between food access and obesity, I
+# thought I'd look at how obesity is affected by poverty. I created a
+# scatterplot to reflect that, and choose geom_jitter since many points
+# overlapped. Then I drew a best fit line. For the Shiny app, I want to see how
+# the different variables affect the mean obesity rate, so I thought I would
+# create graphs reflecting each variable. Having x = age is just a sample of my
+# code to see if it works, and then I'll allow the user to choose the x variable
+# in the Shiny app. Then I saved the plot using ggsave.
 
@@
 
+ggsave("obesity_shiny/plots/poverty_obesity_plot.png", plot = last_plot())
+
 joined_demo <- bootstrap_joined %>% 
@@
        y = "Mean Obesity Rate")
+
+```
+
+```{r food access us map}
+
+# I wanted to plot onto a US map food insecurity, so I used plot_usmap. Then I saved it.
+
+lia_usmap <- plot_usmap(data = food_sum, values = "perc_lia", color = "dark green", labels = FALSE) +
+    theme(legend.position = "right",
+          plot.title = element_text(hjust = 0.5)) + 
+    scale_fill_continuous(low = "white", high = "dark green", name = "Percent of Population") +
+    labs(title = "Percent of Population (age 18+) Classified as Having Low Income and Low Food Access",
+         caption = "Data from USDA and 2010 Census Bureau") +
+    theme_void()
+
+ggsave("obesity_shiny/plots/lia_usmap.png", plot = last_plot())
+
+```
+
+```{r poverty and food access plot}
+
+# I wanted to find the relationship between poverty and food insecurity
+# depending on ruralness, so I graphed it. Then I saved it.
+
+poverty_lia_chart <- bootstrap_joined %>% 
+  ggplot(aes(x = mean_poverty, y = perc_lia)) +
+      geom_jitter(color = "dark green") +
+      theme_minimal() +
+      theme(panel.grid.minor.y = element_blank(),
+            panel.grid.minor.x = element_blank()) +
+       labs(title = "Relationship Between Poverty Rate and Low Income and Low Food Access",
+            caption = "Data from US Department of Agriculture and 2010 Census Bureau",
+            x = "Mean Poverty Rate",
+            y = "Percent of Population Classified as \n Having Low Income and Low Food Access") +
+       geom_smooth(method = "lm", color = "green")
+
+ggsave("obesity_shiny/plots/poverty_lia_chart.png", plot = last_plot())
 

### 2020-04-27 obesity_shiny/app.R

@@ -15,6 +15,7 @@ library(ggplot2)
 library(usmap)
 library(shinyWidgets)
 library(ggcorrplot)
+library(usmap)
 
 # read in data from RDS
 
@@ -23,13 +24,8 @@ joined_cor <- readRDS("data/joined_cor.RDS")
 bootstrap_joined <- readRDS("data/bootstrap_joined.RDS")
 joined <- readRDS("data/joined.RDS")
 food_poverty_mean <- readRDS("data/food_poverty_mean.RDS")
-
-bootstrap_joined <- bootstrap_joined %>%
-    mutate(age = as.factor(age),
-           gender = as.factor(gender),
-           race = as.factor(race),
-           urban = as.factor(urban))
-# filter(!is.na(input$demographic))
+food_sum <- readRDS("data/food_sum.RDS")
+food_lia <- readRDS("data/food_lia.RDS")
 
 # ui code
 
@@ -205,7 +201,8 @@ ui <- navbarPage(
                         br(),
                         
                         selectInput("urban", tags$b("Ruralness:"),
-                                    choices = c("urban", "rural"),
+                                    choices = c("Urban" = "urban", 
+                                                "Rural" = "rural"),
                                     multiple = FALSE)
                         
                     ),
@@ -237,8 +234,101 @@ ui <- navbarPage(
                )
                )),
                
-                tabPanel("Food Access"
+                tabPanel("Food Access",
+                         
+                    tabsetPanel(
+                        tabPanel("The United States",
+                                 
+                                 br(),
+                                 
+                                 fluidRow(
+                                     column(3),
+                                     
+                                     column(6,
+                                            
+                                            br(),
+                                            
+                                            h3("Food Insecurity in the US", style = "color: darkgreen; text-align: center"),
+                                            
+                                            br(),
+                                            
+                                            p("Given the map on the US's increasing obesity rates overtime (under the 'The United States' tab), 
+                                       I thought it would be nice to compare a map that examines the US's food insecurities as well. 
+                                       Looking at the two maps together, it is interesting to see which states have darker colors on both. 
+                                       Which states seem to correlate in the obesity rate map and the food insecurity map?"),
+                                     
+                                 )),
+                        
+                             fluidRow(
+                                imageOutput("lia_usmap")
                         )
+                        ),
+                        
+                        tabPanel("States",
+                                 
+                                 br(),
+                                 br(),
+                                 
+                                 sidebarLayout(
[…]
